%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}\label{intro}

 Genetic Algorithm (GA) is a well-known meta-heuristic that is used to seek solutions given a search space. The GA commonly relies on operators such as the crossover operator, the mutation operator and the selection operator. Each of these operators have their own and specific role in the GA.
 
  The selection operator selects solutions to compose the next generation given their measured fitness function quality value, with higher solutions having higher probability to compose the next generation. The crossover operator generates new solutions by recombining the genetic materials of pairs of individuals to generate new offspring. The mutation operator is applied to the population to sustain diversity, by changing the value of a gene. Both crossover and mutation operators are applied to explore new points in the search space~\cite{blickle1995mathematical}.

One of the most used selection operator is the tournament selection operator. It selects individuals based on their fitness value and on a given parameter, named the tournament size. Controlling the tournament size parameter is one way of adjusting the balance between the exploration and exploration~\cite{blickle1995mathematical}, which governs the search process in GA. Although, it is a very important balance, it cannot be set precisely~\cite{filipovic2012fine}. The selection pressure of tournament selection is expected to increase as the tournament size becomes larger. In other words, the higher the selection pressure, the more the better individuals influences the next generation~\cite{miller1995genetic}. 

As a rule of thumb, small values, such as 2 or 3, are widely used, with small selection pressure and may be good choices, but,very often, the search process converges too slow with smaller tournament size (and too fast with bigger tournament size).~\cite{filipovic2012fine}.

%Very often, the search process converges too slow with smaller tournament size and too fast with bigger tournament size
 
 We would like to reconsider the idea that exists a relationship between exploration versus exploitation and the tournament size parameter by verifying, experimentally, the real impact of the tournament size on the Genetic Algorithm.
 
 Consequently, our goal in this paper, is to observe the performance of the tournament selection in a real-valued Genetic Algorithm. For that we applied the Genetic Algorithm to 24 noise-free BBOB benchmark functions with 10, 20 and 40 dimensions~\cite{hansen2010real}. We explore the number of individuals to be selected by the Tournament operator, with values from 2 to 25.. Then we analyze the results to verify any relationship among the tournament size value, the benchmark functions, and the performance. We also explore briefly the idea that the value of the tournament size value had different effects at different points in the algorithm.

%TODO: Add here the referes for "from the literature
 From the literature, it is possible to understand that there is a preference to small values for the tournament size, as 2 or 3 ~\cite{goldberg1991real, goldberg1993toward, agrawal1995simulated, harik1999gambler, tsutsui1999multi, harik1999compact, deb2000efficient, beyer2001self,kaelo2007integrated, bhunia2009application,  nicolau2009application, sawyerr2011comparative, sawyerr2015benchmarking}. We could trace back to 1991, and we found out that even from that time is has been a popular choice. However, we must highlight that these values are chosen arbitrarily and has small scientific justification. For instance, in 2009, Nicolau used a more pragmatic approach and set an empirical equation to his binary GA. 
 
 

%TODO:
%change this when the scope is complete
These things are described here and there. we do this and that here and there too. results and other stuff are here and there.